Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-07 2020/JPDC_MCO/2020_JPDC.tex
правки статьи

The approach proposed in this paper assumes that the computational values of any function of the same MGO problem can be recalculated to the values of any other functions of the set without any time consuming calculations. In such cases, all the search information obtained in solving a particular problem can be used in solving all other problems in the set. Such repeated reuse of search information can significantly reduce the amount of computation performed, up to just a few iterations when solving the next GO problems. In addition, the presence of informational connectivity significantly expands the possibilities of a parallel solution for MGO problems. The paper proposes two new parallel computational schemes: a cooperative scheme, which means the search information between the problems is exchanged between computational devices with distributed memory used for solving several GO problems in parallel, and a competitive scheme, which occurs when GO problems solved in parallel compete with each other for the use of available computational resources with shared memory.

@@

A key condition of this approach is the assumption that any calculated value of any function $f_i(y)$, $1 \leq i \leq s$, of the set F at an arbitrary point $y \in D$ of the search domain $D$ can be transformed to the value of any other function of the set $F$ at the same point $y \in D$ without any time consuming computations, in a time significantly shorter compared to the computation time values of the functions $f_i(y)$, $1 \leq i \leq s$. In other words, there must be a transformation $Z$ such that
\begin{equation}\label{eq:5}
\begin{matrix}
\forall 1 \leq i, j \leq s, \bar{y} \in D \Rightarrow z_i=Z(z_j ), z_i = f_i (\bar{y}),z_j=f_j (\bar{y}), \\
T(Z) \ll T(f_l (y) ),1 \leq l \leq s,
\end{matrix}
\end{equation}
where $T(*)$  is the computation time of the expression given in parenthesis.

@@

To find efficient (unimprovable) solutions, a widely used approach is based on the reduction (scalarization) of the vector criterion $g(y)$ to the general scalar criterion, the minimization of which will lead to the Pareto optimal solution of the MCO problem \cite{c29,c30,c31,c32,c33}. So, when using mini-max convolution, the vector criterion $g(y)$ from (\ref{eq:6}) reduces to the scalar criterion
\begin{equation}\label{eq:7}
\begin{matrix}
G(\lambda,y)=\max{(\lambda_l g_l(y),1 \leq l \leq m)},	\\
\lambda=(\lambda_1,\lambda_2,\dots,\lambda_m)\in \Lambda \subset R^m:\sum_{l=1}^m{\lambda_l =1},\lambda_l\geq 0,1 \leq l \leq m.
\end{matrix}
\end{equation}

@@

The ability to quickly convert the calculated values of optimized functions determines the need to accumulate and use search information obtained in the calculation process
\begin{equation}\label{eq:9}
\omega_k (j)=\{(y^i,f^i=f_j(y^i)):1 \leq i \leq k \},1 \leq j \leq s,
\end{equation}
where $j$, $1 \leq j \leq s$, is the number of the current function being minimized $f_j (y)$ of the set $F$ from (\ref{eq:3}), $k$ is the number of iterations of the global search, $y^i \in D$, $1 \leq i \leq k$,  are points in which the values of the optimized problems of the set $F$ were computed, and $f^i$, $1 \leq i \leq k$, are the values of the function $f_j (y)$ at these points (the procedure for calculating the value of the function will be called a trial). Global optimization methods can use this search information, thereby ensuring the ability to solve each successive problem of the $F$ set, taking into account the results of all previous calculations. Numerical experiments that were performed (see Section \ref{sec:5}), confirm that such repeated use of search information reduces the number of iterations of the global search required to solve the next problem of the set $F$ (even to the point of performing just a few search iterations).

@@

In accordance with this theory, first of all, dimensionality reduction is achieved using the Peano space-filling curves (evolvents) $y(x)$, uniquely and continuously mapping the interval [0,1] to the $N$-dimensional domain $D$ -- see, for example, \cite{c6,c23}. As a result of this reduction, multidimensional global optimization problems (\ref{eq:1})-(\ref{eq:2}) can be reduced to one-dimensional ones:

@@

\begin{equation}\label{eq:14}
x_1< x_2< \cdots < x_k
\end{equation}
or a more efficient execution of global search algorithms. It should be noted that in optimizing the reduced one-dimensional functions $f_i (y(x))$, $1 \leq i \leq s$, many one-dimensional global search algorithms can be used (possibly after some generalization).

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig1}
  \caption{Examples of approximations of the Peano space-filling curves (the approximation density is equal to 2, 3 and 4 correspondingly) \cite{c6}}
  \label{fig:1}
\end{figure}

@@

	\State Calculate the stop condition
	\begin{equation}\label{eq:22}
     stop = \begin{cases} true, &(x_t - x_{t-1})^{1/N} \leq \varepsilon,\\
		                      false,&(x_t - x_{t-1})^{1/N} > \varepsilon.
							\end{cases}		
  \end{equation}
  \If{ \textbf{not} $stop$}
	  \State Calculate $z^{k+1} = f( y(x^{k+1}))$;
    \State Insert $(x^{k+1}, y(x^{k+1}), z^{k+1})$ into the search information $A_k$;
    \State Increase $k = k + 1$;
  \EndIf
\EndWhile
\State Find the estimate of the global minimum point
\begin{equation}\label{eq:23}
y_k^*= y(x_l),  z_k^*=z_l,
\end{equation}
where $l= \argmin_{1 \leq i \leq k}z_i$.
\State \textbf{return} $y_k^*$, $z_k^*$, $k$;
\end{algorithmic}
\end{algorithm}

@@

In the framework of the proposed approach, the GSA algorithm described above will be used to solve global optimization problems of the set $F$. Moreover, due to the informational connectivity (\ref{eq:5}) of the problems of the set $F$, the search information $A_k$ can be quickly transformed to the values of the next function to be minimized $f(y)$ of the set $F$ and GSA can minimize each successive function $f(y)$, taking into account the results of all previous calculations. The GSA algorithm for solving problems of the set $F$ and using search information $A_k$, will be referred to as the multiple global search algorithm (MGSA).

@@

In the framework of the information-statistical theory, a general approach to parallelizing global optimization problems has been proposed -- parallel computing is provided by parallel (simultaneous) computing of the values of the minimized function at several different points in the search domain. This approach is general -- it can be applied to solving any global optimization problems in a parallel mode. And such an approach is efficient, since the most time consuming part of the problem is parallelized due to the initial assumption that calculating the values of functions to be minimized is computationally expensive.

@@

Input data of this algorithm are the set of functions $F(y)$ from (\ref{eq:3}), search domain $D$ from (\ref{eq:2}), reliability parameter $r>1$, required accuracy $\varepsilon > 0$, maximum possible number of calculations of the values of the functions to be minimized $kmax$ and the number of available computational devices ({cores/processors}) with shared memory $q>1$. The results of executing the algorithm are the sets of estimates of global minimum points of the functions being minimized $Y$ and values of the functions $Z$ in these points, and the total number of executed iterations of global search $k$. As before, in the course of calculations we use the search information $A_k$, which contains the points of earlier iterations of global search $x_i$, $1 \leq i \leq k$, ordered in ascending order, and values of the current function being minimized $z_i=f(y(x_i))$, $1 \leq i \leq k$.

@@

It should also be noted that when implementing this approach to compare the interval characteristics in different global optimization problems, the values of the function being minimized in the available search information should be normalized\footnote{After transformation (\ref{eq:25}), $z_k^*=0$ and $m_k=1$ are carried out for all $ns$ parallel problems.}
\begin{equation}\label{eq:25}
z(is)_i'=\frac{z(is)_i - z(is)_k^*}{m(is)_k}, 1 \leq i \leq k,1 \leq is \leq ns,
\end{equation}
where $z(is)_k$, $1 \leq is \leq ns$, are the estimates (\ref{eq:23}) of the minimum values of the functions being minimized, and $m(is)_k$, $1 \leq is \leq ns$, are the estimates (\ref{eq:19}) of the H\"older constants $H_{is}$, $1 \leq is \leq ns$, from (\ref{eq:12}). Further, when performing the steps of the algorithm, the converted values $z(is)_i'$, $1 \leq i \leq k$, $1 \leq is \leq ns$, should be used when calculating the characteristics of intervals and points of new iterations of the global search.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{fig3}
  \caption{An example of intervals selection by the PMGSA-2 algorithm (Step 1)}
  \label{fig:3}
\end{figure}

@@

1) At the end of each parallel iteration of the global search, the results of the iteration $(x^{k+j},z^{k+j} )$, $1 \leq j \leq q$, of each node are transferred to all available computational nodes with the necessary recalculation of the values of functions being minimized in accordance with the transformation $Z$ from (\ref{eq:5}).

2) Before performing a new iteration, each computational node accepts the search data transmitted to it and adds this data to the search information $A_k (is)$, $1\leq is \leq q$, from (\ref{eq:13}).

@@

Numerical experiments were performed on the supercomputers Lobachevsky (University of Nizhni Novgorod) and Endeavour (Intel Cluster). The first supercomputer was used for optimization software system. The numerical results were obtained by the second one with the following computational nodes: 2 Intel Xeon Platinum 8260L, 2.4 GHz, 256 GB RAM (i.e. a total of 48 CPU cores were available on each node). The executable program code was built by using the Intel Parallel Studio XE 2019 software package. The numerical experiments were performed using the Globalizer system \cite{c36}. This system offers an opportunity to solve computationally intensive multicriteria multiextremal optimization problems using the parallel global search algorithms presented in the paper.

@@

\begin{table}[ht]
\centering
\caption{Comparison of the effectiveness of multicriteria optimization algorithms)}
\label{tab:1}
\begin{tabular}{cccccc}
\hline
Method                                                                                     & MC    & SEMO  & NUC   & BLO   & \textbf{MGSA} \\ \hline
Iteration number                                          & 500   & 500   & 515   & 498   & \textbf{370}   \\
\begin{tabular}[c]{@{}c@{}}Number of Pareto optimal points\end{tabular} & 67    & 104   & 29    & 68    & \textbf{100}    \\
HV                                                        & 0.300 & 0.312 & 0.306 & 0.308 & \textbf{0.316} \\
DU                                                        & 1.277 & 1.116 & 0.210 & 0.175 & \textbf{0.101} \\ \hline
\end{tabular}
\end{table}

@@

The results of the numerical experiments are presented in Table \ref{tab:2}. The first three rows of the Table contain information about the computational resources used during the experiments. The first row marked as ``$p$'' indicates the number of computational nodes used. The number of cores used within a single node is presented in the second row marked as ``$q$''. The total number of cores used is presented in the third row marked as ``$p*q$''. The rows four through six show the average number of iterations performed by PMGSA-1,2,3 for solving a single MCO problem accordingly.

@@

In the second series of the experiments, the problems being solved were made more complicated by increasing the dimensionality -- the five-criterion six-dimensional MCO problem was solved, i.e., $N = 6$, $m = 5$. For solving these problems the parallel PMGSA-3 method was applied. When performing the experiments, the accuracy of the method $\varepsilon = 0.1$ and the reliability of the method $r = 5.6$ were used. The results of the experiments are presented in Table \ref{tab:3}.

@@

\begin{table}[]
\centering
\caption{Results of numerical experiments to solve the applies problem}
\label{tab:4}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccccc}
\hline
Computational                     & p                     & 1       & 1      & 1       & 1       & 5       \\
resources                         & q                     & 1       & 1      & 48      & 48      & 48      \\
used                              & p*q                   & 1       & 1      & 48      & 48      & 240     \\ \hline
\multicolumn{2}{c}{Method}                                & GSA     & MGSA   & PMGSA-1 & PMGSA-2 & PMGSA-3 \\
\multicolumn{2}{c}{Iterations}                            & 703,802 & 13,120 & 403     & 237     & 116     \\
\multicolumn{2}{c}{HV}                                    & 1.46    & 1.45   & 1.38    & 1.88    & 1.39    \\
\multicolumn{2}{c}{DU}                                    & 501.03  & 499.43 & 500.46  & 498.73  & 500.39  \\
\multicolumn{2}{c}{Speedup}                               & -       & 1      & 32.6    & 55.4    & 113.1   \\
\multicolumn{2}{c}{\begin{tabular}[c]{@{}c@{}}Overall reduction \\ of iteration number\end{tabular}} & 1       & 53.6   & 1,746.4 & 2,969.6 & 6,067.3 \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}

@@

The availability of informational connectivity significantly expands the possibilities of parallel solutions of the entire set of multiple global optimization problems. The paper proposes two parallel computational schemes: a cooperative scheme, which means the search information between the problems is exchanged between computational devices with distributed memory used for solving several GO problems in parallel, and a competitive scheme, which occurs when GO problems solved in parallel compete with each other for the use of available computational resources with shared memory..

>>>>

The approach proposed in this paper assumes that the computational values of any function of the same MGO problem can be recalculated to the values of any other functions of the set without any time consuming calculations. In such cases, all the search information obtained in solving a particular problem can be used in solving all other problems in the set. Such repeated reuse of search information can significantly reduce the amount of computation performed, up to just a few iterations when solving the next GO problems. In addition, the presence of informational connectivity significantly expands the possibilities of a parallel solution for MGO problems. The paper proposes two new parallel computational schemes: a cooperative scheme, which means the search information is exchanged between computational devices with distributed memory used for solving several GO problems in parallel, and a competitive scheme, which occurs when GO problems solved in parallel compete with each other for the use of available computational resources with shared memory.

@@

A key condition of this approach is the assumption that any calculated value of any function $f_i(y)$, $1 \leq i \leq s$, of the set $F$ at an arbitrary point $y \in D$ of the search domain $D$ can be transformed to the value of any other function of the set $F$ at the same point $y \in D$ without any time consuming computations, in a time significantly shorter compared to the computation time values of the functions $f_i(y)$, $1 \leq i \leq s$. In other words, there must be a transformation $Z$ such that
\begin{equation}\label{eq:5}
\begin{matrix}
\forall 1 \leq i, j \leq s, \bar{y} \in D \Rightarrow z_i=Z(z_j ), z_i = f_i (\bar{y}),z_j=f_j (\bar{y}), \\
T(Z) \ll T(f_l (y) ),1 \leq l \leq s,
\end{matrix}
\end{equation}
where $T(*)$  is the computation time of the expression given in parenthesis.

@@

To find efficient (unimprovable) solutions, a widely used approach is based on the reduction (scalarization) of the vector criterion $g(y)$ to the general scalar criterion, the minimization of which will lead to the Pareto optimal solution of the MCO problem \cite{c29,c30,c31,c32,c33}. So, when using minimax convolution, the vector criterion $g(y)$ from (\ref{eq:6}) reduces to the scalar criterion
\begin{equation}\label{eq:7}
\begin{matrix}
G(\lambda,y)=\max{(\lambda_l g_l(y),1 \leq l \leq m)},	\\
\lambda=(\lambda_1,\lambda_2,\dots,\lambda_m)\in \Lambda \subset R^m:\sum_{l=1}^m{\lambda_l =1},\lambda_l\geq 0,1 \leq l \leq m.
\end{matrix}
\end{equation}

@@

The ability to quickly convert the calculated values of optimized functions determines the need to accumulate and use search information obtained in the calculation process
\begin{equation}\label{eq:9}
\omega_k (j)=\{(y^i,f^i=f_j(y^i)):1 \leq i \leq k \},1 \leq j \leq s,
\end{equation}
where $j$, $1 \leq j \leq s$, is the number of the current function being minimized $f_j (y)$ of the set $F$ from (\ref{eq:3}), $k$ is the number of iterations of the global search, $y^i \in D$, $1 \leq i \leq k$,  are points in which the values of the optimized problems of the set $F$ were computed, and $f^i$, $1 \leq i \leq k$, are the values of the function $f_j (y)$ at these points (the procedure for calculating the value of the function will be called a trial). Global optimization methods can use this search information, thereby ensuring the ability to solve each successive problem of the set $F$, taking into account the results of all previous calculations. Numerical experiments that were performed (see Section \ref{sec:5}), confirm that such repeated use of search information reduces the number of iterations of the global search required to solve the next problem of the set $F$ (even to the point of performing just a few search iterations).

@@

In accordance with this theory, first of all, dimensionality reduction is achieved using the Peano space-filling curves (evolvents) $y(x)$, uniquely and continuously mapping the interval [0,1] to the $N$-dimensional domain $D$ -- see, for example, \cite{c6,c23}. As a result of this reduction, multidimensional global optimization problems (\ref{eq:1})-(\ref{eq:3}) can be reduced to one-dimensional ones:

@@

\begin{equation}\label{eq:14}
x_1< x_2< \cdots < x_k
\end{equation}
for a more efficient execution of global search algorithms. It should be noted that in optimizing the reduced one-dimensional functions $f_i (y(x))$, $1 \leq i \leq s$, many one-dimensional global search algorithms can be used (possibly after some generalization).

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig1}
  \caption{Examples of approximations of the Peano space-filling curves (the approximation density is equal to 2, 3 and 4 correspondingly)}
  \label{fig:1}
\end{figure}

@@

	\State Check the stopping condition
	\begin{equation}\label{eq:22}
     stop = \begin{cases} true, &(x_t - x_{t-1})^{1/N} \leq \varepsilon,\\
		                      false,&(x_t - x_{t-1})^{1/N} > \varepsilon.
							\end{cases}		
  \end{equation}
  \If{ \textbf{not} $stop$}
	  \State Calculate $z^{k+1} = f( y(x^{k+1}))$;
    \State Insert $(x^{k+1}, y(x^{k+1}), z^{k+1})$ into the search information $A_k$;
    \State Increase $k = k + 1$;
  \EndIf
\EndWhile
\State Find the estimate of the global minimum point
\begin{equation}\label{eq:23}
y_k^*= y(x_l),  z_k^*=z_l,
\end{equation}
where $l= \argmin_{1 \leq i \leq k}z_i$.
\State \textbf{return} $y_k^*$, $z_k^*$, $k$;
\end{algorithmic}
\end{algorithm}

@@

In the framework of the proposed approach, the GSA algorithm described above will be used to solve global optimization problems of the set $F$. Moreover, due to the informational connectivity (\ref{eq:5}) of the problems of the set $F$, the search information $A_k$ can be quickly transformed to the values of the next function to be minimized $f(y)$ of the set $F$ and GSA can minimize each successive function $f(y)$, taking into account the results of all previous calculations. The GSA algorithm for solving GO problems of the set $F$ and using search information $A_k$, will be referred to as the \textit{Multiple Global Search Algorithm} (MGSA).

@@

In the framework of the information-statistical theory, a general approach to parallelizing global optimization problems has been proposed -- parallel computing is provided by parallel (simultaneous) computing of the values of the minimized function at several different points in the search domain. This approach is general -- it can be applied to solving any global optimization problems in a parallel mode. And such an approach is efficient, since the most time consuming part of computations is parallelized due to the initial assumption that calculating the values of functions to be minimized is computationally expensive.

@@

Input data of this algorithm are the set of functions $F(y)$ from (\ref{eq:3}), the search domain $D$ from (\ref{eq:2}), the reliability parameter $r>1$, the required accuracy $\varepsilon > 0$, the maximum possible number of calculations of the values of the functions to be minimized $kmax$ and the number of available computational devices ({cores/processors}) with shared memory $q>1$. The results of executing the algorithm are the sets of estimates of global minimum points of the functions being minimized $Y$ and values of the functions $Z$ at these points, and the total number of executed iterations of global search $k$. As before, in the course of calculations we use the search information $A_k$, which contains the points of earlier iterations of global search $x_i$, $1 \leq i \leq k$, ordered in ascending order, and values of the current function being minimized $z_i=f(y(x_i))$, $1 \leq i \leq k$.

@@

It should also be noted that when implementing this approach to compare the interval characteristics in different global optimization problems, the values of the function being minimized in the available search information should be normalized\footnote{After transformation (\ref{eq:25}), $z_k^*=0$ and $m_k=1$ are carried out for all $ns$ parallel problems.}
\begin{equation}\label{eq:25}
z(is)_i'=\frac{z(is)_i - z(is)_k^*}{m(is)_k}, 1 \leq i \leq k,1 \leq is \leq ns,
\end{equation}
where $z(is)_k^*$, $1 \leq is \leq ns$, are the estimates (\ref{eq:23}) of the minimum values of the functions being minimized, and $m(is)_k$, $1 \leq is \leq ns$, are the estimates (\ref{eq:19}) of the H\"older constants $H_{is}$, $1 \leq is \leq ns$, from (\ref{eq:12}). Further, when performing the steps of the algorithm, the converted values $z(is)_i'$, $1 \leq i \leq k$, $1 \leq is \leq ns$, should be used when calculating the characteristics of intervals and points of new iterations of the global search.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{fig3}
  \caption{An example of intervals selection by the PMGSA-2 algorithm}
  \label{fig:3}
\end{figure}

@@

3) At the end of each parallel iteration of the global search, the results of the iteration $(x^{k+j},z^{k+j} )$, $1 \leq j \leq q$, of each node are transferred to all available computational nodes with the necessary recalculation of the values of functions being minimized in accordance with the transformation $Z$ from (\ref{eq:5}).

4) Before performing a new iteration, each computational node accepts the search data transmitted to it and adds this data to the search information $A_k (is)$, $1\leq is \leq q$, from (\ref{eq:13}).

@@

Numerical experiments were performed on the supercomputers Lobachevsky (University of Nizhni Novgorod) and Endeavour (Intel Cluster). The first supercomputer was used for optimization software system development. The numerical results were obtained by the second one with the following computational nodes: 2 Intel Xeon Platinum 8260L, 2.4 GHz, 256 GB RAM (i.e. a total of 48 CPU cores were available on each node). The executable program code was built by using the Intel Parallel Studio XE 2019 software package. The numerical experiments were performed using the Globalizer system \cite{c36}. This system offers an opportunity to solve computationally intensive multicriteria multiextremal optimization problems using the parallel global search algorithms presented in the paper.

@@

\begin{table}[ht]
\centering
\caption{Comparison of the effectiveness of multicriteria optimization algorithms}
\label{tab:1}
\begin{tabular}{cccccc}
\hline
Method                                                                                     & MC    & SEMO  & NUC   & BLO   & \textbf{MGSA} \\ \hline
Iteration number                                          & 500   & 500   & 515   & 498   & \textbf{370}   \\
\begin{tabular}[c]{@{}c@{}}Number of Pareto optimal points\end{tabular} & 67    & 104   & 29    & 68    & \textbf{100}    \\
HV                                                        & 0.300 & 0.312 & 0.306 & 0.308 & \textbf{0.316} \\
DU                                                        & 1.277 & 1.116 & 0.210 & 0.175 & \textbf{0.101} \\ \hline
\end{tabular}
\end{table}

@@

The results of the numerical experiments are presented in Table \ref{tab:2}. The first three rows of the Table contain information about the computational resources used during the experiments. The first row marked as ``$p$'' indicates the number of computational nodes used. The number of cores used within a single node is presented in the second row marked as ``$q$''. The total number of cores used is presented in the third row marked as ``$p*q$''. The rows four through six show the average number of iterations performed by PMGSA-1,2,3 for solving a single MCO problem (i.e., 100 GO problems) accordingly.

@@

In the second series of the experiments, the problems being solved were made more complicated by increasing the dimensionality -- the five-criterion six-dimensional MCO problem was solved, i.e., $N = 6$, $m = 5$. For solving these problems the parallel PMGSA-3 method was applied. When performing the experiments, the accuracy $\varepsilon = 0.1$ and the reliability $r = 5.6$ were used. The results of the experiments are presented in Table \ref{tab:3}.

@@

\begin{table}[]
\centering
\caption{Results of numerical experiments to solve the applied problem}
\label{tab:4}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccccc}
\hline
Computational                     & p                     & 1       & 1      & 1       & 1       & 5       \\
resources                         & q                     & 1       & 1      & 48      & 48      & 48      \\
used                              & p*q                   & 1       & 1      & 48      & 48      & 240     \\ \hline
\multicolumn{2}{c}{Method}                                & GSA     & MGSA   & PMGSA-1 & PMGSA-2 & PMGSA-3 \\
\multicolumn{2}{c}{Iterations}                            & 703,802 & 13,120 & 403     & 237     & 116     \\
\multicolumn{2}{c}{HV}                                    & 1.46    & 1.45   & 1.38    & 1.88    & 1.39    \\
\multicolumn{2}{c}{DU}                                    & 501.03  & 499.43 & 500.46  & 498.73  & 500.39  \\
\multicolumn{2}{c}{Speedup}                               & -       & 1      & 32.6    & 55.4    & 113.1   \\
\multicolumn{2}{c}{\begin{tabular}[c]{@{}c@{}}Overall reduction \\ of iteration number\end{tabular}} & 1       & 53.6   & 1,746.4 & 2,969.6 & 6,067.3 \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}

@@

The availability of informational connectivity significantly expands the possibilities of parallel solutions of the entire set of multiple global optimization problems. The paper proposes two parallel computational schemes: a cooperative scheme, which means the search information between the problems is exchanged between computational devices with distributed memory used for solving several GO problems in parallel, and a competitive scheme, which occurs when GO problems solved in parallel compete with each other for the use of available computational resources with shared memory.
